### 2012-08-27 intention motor representation joint action (paper 3)/conf collective intentionality manchester 2012/motor representation and shared intention.tex
final version? Monday's effort

\section{Intention and Motor Representation}
So that you can see where this is going, let me briefly explain what stands behind the view that motor representation is needed in addition to intention in saying which events are actions.

@@

If we appeal to a notion of shared intention,
we can answer these questions about joint action in a way that is superficially similar to way we answered the parallel questions about ordinary, individual action.
A shared intention is what relates purposive joint actions to the outcomes to which they are directed.
For the shared intention 
involves a representation, on the part of each agent, of an outcome,
coordinates the several agents’ activities
and 
coordinates the several agents’ activities in such a that would normally facilitate the occurrence of the represented outcome.
This is how a shared intention can bind together the activities comprising a joint action and link them to an outcome.
%Shared intention does for joint action roughly what ordinary intention does for ordinary, individual action.

>>>>

\section{Intention and Motor Representation}
[\emph{*Probably skip all of this section in the talk}]

So that you can see where this is going, let me briefly explain what stands behind the view that motor representation is needed in addition to intention in saying which events are actions.

@@

If we appeal to a notion of shared intention,
we can answer these questions about joint action in a way that is superficially similar to way we answered the parallel questions about ordinary, individual action.
A shared intention is what relates purposive joint actions to the outcomes to which they are directed.
For the shared intention 
involves a representation, on the part of each agent, of an outcome,
coordinates the several agents’ activities
and 
coordinates the several agents’ activities in such a way that would normally facilitate the occurrence of the represented outcome.
This is how a shared intention can bind together the activities comprising a joint action and link them to an outcome.
%Shared intention does for joint action roughly what ordinary intention does for ordinary, individual action.
